Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-07-06 Final_Manuscript.tex
added correlations with auth items

\subsection{Combining Samples}\label{combining-samples}

Data from two different, but demographically equivalent, samples were
combined to create the final analysis sample (\emph{N =} 64) used in
this study. In the measures section that follows we refer to them as
Sample 1 and Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal
arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
women's liberal arts college in the northeast US. The results section
contains more detail about equivalence analyses to support the decision
to combine these two samples.

@@

Thirty-two previously unacquainted self-identifying female-sex dyads (64
total participants) from two liberal arts institutions in the Northeast
of the United States participated in this study. More specifically,
twelve of the pairs, which derived from Sample 1, were students at a
co-ed liberal arts college, while the remaining twenty pairs who came
from Sample 2 attended a women's liberal arts college. Initially, data
was collected from same-sex and mixed-sex dyads that comprised of male
and female gendered individuals. Sample 1 originally consisted of
twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs
made up of forty-three women and one man, as well as two participants
who did not identify with either gender category, formed Sample 2. Due
to similarities across samples in regard to correlation patterns between
significant variables within this study, the two datasets were combined.
For consistency, we limited participant data to same sex female pairs at
the two colleges. These participants were mostly first-year college
students, with an average age of 18.85 (SD = 1.04). The sample was
48.44\% White/European American, 9.38\% Black/African-American, 28.12\%
Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
8 White/White pairs and 4 same race racial minority pairs, for a total
of 12 same-race pairs. The remaining 20 were mixed race pairs, of which
15 were White/racial minority pairings and 5 were cross-racial minority
group pairs. 64.06\% of the sample identified as heterosexual, and 25\%
identified as gay, lesbian or bisexual.

@@

\subsubsection{Combining Samples}\label{combining-samples-1}

>>>>

\subsection{Combined Samples}\label{combined-samples}

Data from two different, but demographically equivalent, samples were
combined to create the final analysis sample (\emph{N =} 64) used in
this study. In the measures section that follows we refer to them as
Sample 1 and Sample 2. Sample 1 (\emph{N =} 24) is from a co-ed liberal
arts college in the northeast US and Sample 2 (\emph{N =} 40) is from a
women's liberal arts college in the northeast US. The description of the
samples section below contains more detail about equivalence analyses to
support the decision to combine these two samples.

@@

Thirty-two previously unacquainted self-identifying female-sex dyads (64
total participants) from two liberal arts institutions in the Northeast
of the United States participated in this study. More specifically,
twelve of the pairs, which derived from Sample 1, were students at a
co-ed liberal arts college, while the remaining twenty pairs who came
from Sample 2 attended a women's liberal arts college. Initially, data
was collected from same-sex and mixed-sex dyads that comprised of male
and female gendered individuals. Sample 1 originally consisted of
twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs
made up of forty-three women and one man, as well as two participants
who did not identify with either gender category, formed Sample 2. For
consistency, we limited participant data to same sex female pairs at the
two colleges.

There were some similar correaltions bewtween study variables across
samples.

Due these similarities across samples in regard to correlation patterns
between significant variables within this study, the two datasets were
combined. These participants were mostly first-year college students,
with an average age of 18.85 (SD = 1.04). The sample was 48.44\%
White/European American, 9.38\% Black/African-American, 28.12\%
Asian/Pacific Islander, 9.38\% Latinx, and 4.69\% mixed-race. There were
8 White/White pairs and 4 same race racial minority pairs, for a total
of 12 same-race pairs. The remaining 20 were mixed race pairs, of which
15 were White/racial minority pairings and 5 were cross-racial minority
group pairs. 64.06\% of the sample identified as heterosexual, and 25\%
identified as gay, lesbian or bisexual.

@@

\subsubsection{Combining Samples}\label{combining-samples}
